---
title: "Sea Around Us R Package"
author: "Gordon Tsui"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

To get a list of our geographical regions with associated ids, use `listregions()`.  
A list of our geography options:  
`eez` - Exclusive Economic Zone  
`highseas` - High Seas  
`fao` - FAO Statistical areas  
`lme` - Large marine ecosystem  
`rfmo` - Regional fisheries management organization  
`meow` - Marine ecoregions of the world  
  
`listregions()` can also be used to get ids for:  
`fishing-entity` - Fishing entity (note the column 'id' is the fishing entity id. 'country id' is the geo entity)  
`geo-entity` - additional information about countries but not a filter used in the catch data  
`taxa` - list of our taxa and taxon keys  

```{r}
library(seaaroundus)
head(listregions('eez'))
```


## Catch and Value data

To obtain our catch and landed value data, use `catchdata(<region>, <id>)`.

Accepted regions are:
`eez`  
`lme`  
`rfmo`  
`meow`  

```{r}
library(seaaroundus)
df <- catchdata('eez', 8)
head(df)
```

